CFF GCT Study

### 2025-06-12 Christine Chan/CFF GCT Study/cff_gct_analysis.qmd
started GCT flowchart

```{r setup}
#| include: false
library(readxl)
library(dplyr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(ggpmisc)
library(pROC)
library(rspiro)
library(childsds)
library(arsenal)
library(gt)
library(reporttools)
library(rpart)
library(rpart.plot)
library(rms)
library(patchwork)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/tim/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
  "Linux" = "/home/tim/OneDrive/Vigers/CF"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/tim/Documents/GitHub",
  "Windows" = "C:/Users/Tim/Documents/GitHub",
  "Linux" = "/home/tim/Documents/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

  filter(`OGTT Timepoint` != "OGTT 60 min")

@@

  levels = c("OGTT 0 min", "GCT 60 min plasma", "OGTT 120 min")

@@

@@

>>>>

```{r setup}
#| include: false
library(readxl)
library(dplyr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(ggpmisc)
library(pROC)
library(rspiro)
library(childsds)
library(arsenal)
library(gt)
library(reporttools)
library(rpart)
library(rpart.plot)
library(rms)
library(patchwork)
library(ggflowchart)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/tim/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
  "Linux" = "/home/tim/OneDrive/Vigers/CF"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/tim/Documents/GitHub",
  "Windows" = "C:/Users/Tim/Documents/GitHub",
  "Linux" = "/home/tim/Documents/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

@@

  levels = c("OGTT 0 min", "OGTT 60 min", "OGTT 120 min", "GCT 60 min plasma"),
  labels = c("Fasting", "OGTT-1hG", "OGTT-2hG", "GCTpl")

@@

  scale_fill_manual(values = RColorBrewer::brewer.pal(4, "Set2")) +

@@

# Flowchart

```{r}
flow_df <- tibble(
  from = c(
    "Initial Screen with GCT",
    "Initial Screen with GCT", 
    "GCTpl >= 147",
    "GCTpl < 147"
  ),
  to = c(
    "GCTpl >= 147", 
    "GCTpl < 147", 
    "Oral Glucose Tolerance Test", 
    "Repeat Screen in 1 Year"
  )
)

ggflowchart(flow_df)
```
